### 2013-12-09 results.tex
added variables for pathology correlations

Weights and axis measurements from the gross pathology processing of the
excised prostates were collected (Table~\ref{tab:path_data}), and using the
axis measurements (lateral-to-lateral, anterior-to-posterior, and
apex-to-base), the prostate volume was approximated as a tri-axial ellipsoid,
and its volume was estimated (\ref{eqn:ellipsoid_volume}).  Prostate weights
were moderately correlated with estimated pathology ellipsoidal prostate
volumes (Figure~\ref{fig:mr_arfi_weight}(a), R$^2$ = 0.68).  There was moderate
correlation between the prostate weight and the image-reconstructed prostate
volumes (Figure~\ref{fig:mr_arfi_weight}(b), R$^2$ = 0.44 (MR) and 0.18
(ARFI)), though there was weaker correlation with the ellipsoidal approximation
of the measurement prostate volume and the image-reconstructed volumes
(Figure~\ref{fig:mr_arfi_weight}(c), R$^2$ = 0.08 (MR) and 0.00 (ARFI)).

>>>>

Weights and axis measurements from the gross pathology processing of the
excised prostates were collected (Table~\ref{tab:path_data}), and using the
axis measurements (lateral-to-lateral, anterior-to-posterior, and
apex-to-base), the prostate volume was approximated as a tri-axial ellipsoid,
and its volume was estimated (\ref{eqn:ellipsoid_volume}).  Prostate weights
were moderately correlated with estimated pathology ellipsoidal prostate
volumes (Figure~\ref{fig:mr_arfi_weight}(a), R$^2$ = \pathVolWeightRsq).  There
was moderate correlation between the prostate weight and the
image-reconstructed prostate volumes (Figure~\ref{fig:mr_arfi_weight}(b), R$^2$
= \weightMRrsq~(MR) and \weightARFIrsq~ (ARFI)), though there was weaker
correlation with the ellipsoidal approximation of the measurement prostate
volume and the image-reconstructed volumes (Figure~\ref{fig:mr_arfi_weight}(c),
R$^2$ = \pathVolMRrsq~(MR) and \pathVolARFIrsq~(ARFI)).
